### 2025-01-08 paper/icml25/first/sects/shacpp.tex
minor + related (WIP)

To summarize, our algorithm, aims to minimize the 4 presented losses, $\mathcal{L'}_\theta^{\pi}$, $\mathcal{L}_\theta^V$, $\mathcal{L}_\theta^R$, and $\mathcal{L}_\theta^F$. A minimal pseudocode of our algorithm is presented in \ref{alg:shacpp}. Figure~\ref{fig:shacpp} presents an unrolled view of the \fname{} algorithm.

@@

        \STATE $s,a,r,v \sim \mathcal{E}(\pi)$
        \STATE $\hat{s} = W(s[0], a)$
        \STATE $\hat{r} = R(\hat{s})$
        \STATE $\hat{v} = V(\hat{s})$

        \STATE $\pi_\theta \gets \pi_\theta - \eta_\pi \nabla \mathcal{L'}^\pi_\theta(\hat{r},\hat{v},\gamma,\alpha)$
        \STATE $V_\theta \gets V_\theta - \eta_V \nabla \mathcal{L}^V_\theta(\hat{v},s,v)$
        \STATE $R_\theta \gets R_\theta - \eta_R \nabla \mathcal{L}^R_\theta(\hat{r},s,r)$
        \STATE $F_\theta \gets F_\theta - \eta_F \nabla \mathcal{L}^F_\theta(\hat{s},s,a)$

@@

    \end{algorithmic}
    \caption{SHAC++ minimal (no cache and no cool-down) pseudocode}
    \label{alg:shacpp}
\end{algorithm}

>>>>

To summarize, our algorithm, aims to minimize the 4 presented losses, $\mathcal{L'}_\theta^{\pi}$, $\mathcal{L}_\theta^V$, $\mathcal{L}_\theta^R$, and $\mathcal{L}_\theta^F$. The parameters $\theta$ can be either shared or separated among the different networks, however, we always keep them separated in our experiments. A minimal pseudocode of our algorithm is presented in \ref{alg:shacpp}. Figure~\ref{fig:shacpp} presents an unrolled view of the \fname{} algorithm.

@@

        \STATE $s,a,r,v \sim \mathcal{E}(\pi)$
        \STATE $\hat{s} = F_\theta(s_{:,0}, a)$
        \STATE $\hat{r} = R_\theta(\hat{s})$
        \STATE $\hat{v} = V_\theta(\hat{s})$

        \STATE $\theta \gets \theta - \eta_\pi \nabla \mathcal{L'}^\pi_\theta(\hat{r},\hat{v},\gamma,\alpha)$
        \STATE $\theta \gets \theta - \eta_V \nabla \mathcal{L}^V_\theta(\hat{v},s,v)$
        \STATE $\theta \gets \theta - \eta_R \nabla \mathcal{L}^R_\theta(\hat{r},s,r)$
        \STATE $\theta \gets \theta - \eta_F \nabla \mathcal{L}^F_\theta(\hat{s},s,a)$

@@

    \end{algorithmic}
    \caption{SHAC++ minimal (no cache and no cool-down) pseudocode. $s_{:,0}$ denotes the first step of each trajectory in $s$.}
    \label{alg:shacpp}
\end{algorithm}
